---
title: "simpleRegress"
author: "Gema Garcia"
date: "Summer 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```



The bears neck is 20 inches around which helps predict about 57 in length.The x axis is the size of the bears neck and the y axis is the length. Looking at the second part of data, it shows the residual standard error is 5.376 and the R squared is 0.7476.




```{r}
MYCHEST <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(MYCHEST)
summary.lm(MYCHEST)
```




We see that our residual standard error is 4.939 and our R squared is 0.7869. Comparing our residual standard error of 4.939 to the first one of 5.376, this one is better because it is smaller. Chest is higher in ranking than neck.For R squared values since 0.7869 is bigger than 0.7476, it shows chest is better in both residual standard error and r squared.



```{r}
MYHEADWTH <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(MYHEADWTH)
summary.lm(MYHEADWTH)
```



By looking at it, the way it is spread out already gives it a bad ranking. Our residual standard error is 7.32 and our R squared is 0.5321. This one is at the bottom of our ranking because the standard error is high which is bad and the R squared is too small.




```{r}
MYWEIGHT <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(MYWEIGHT)
summary.lm(MYWEIGHT)
```



Looking at the plot we see the dots follow alongside the line a bit. We see the residual standard error is 5.432 and the R squared is 0.7423. In our ranking this may go in third place since the residual standard error is not the highest (bad) or the lowest (good).




```{r}
MYAGE <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(MYAGE)
summary.lm(MYAGE)
```



Looking at our residual standard error of 7.511 we can already tell this will have a low ranking. The r squared value is 0.5073 and it supports its low ranking because it is just as low as 0.5321 in the headwth.




```{r}
MYHEADLEN <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(MYHEADLEN)
summary.lm(MYHEADLEN)
```






## Compare all models that predict LENGTH other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 

